\chapter{The urgency of the topic}
\label{ch:Topic}

 The situation of Vietnamese derivatives market this year. Derivatives offer bright future for Vietnamese stocks. On August 10, 2017, Vietnam has opened a derivatives market to draw more investment to its capital markets with future contracts. The market will start with two main derivative products which are stock index and government bond futures and once fully operational, more instruments will be introduced. In addition, according to the predict of economic experts, option contract will be operated in Vietnam in December.\\ [0.5cm]
The discourse will respect to the barrier option option which offers the right to buy or sell securities but not the obligation.  The special features here is that payoffs  depends on whether or not the underlying asset price has reached or exceeded some barrier level during the option’s life. The barrier options are popular and attractive thanks to benefits that they give investors more flexibility to express their view on the asset price movement in the option contract. There are some advantages of this option. Firstly, The barrier option depends on the predict of the investor about price of stock in the future, so it is suitable to beliefs about the future behavior of the market. Secondly, it match hedging needs more closely that it helps  the investor reduce risk  because of the fluctuation of prices. Lastly, Premiums are generally low  by not paying a premium to cover scenarios he or she views as unlikely. 


 




