\chapter{Conclusion}
\fontsize{11pt}{20pt}\selectfont 
Currently, the financial market in Vietnam becomes exciting than ever thanks to the launch of Derivatives market which is to complete the stock market and financial market in Vietnam, helping to improve the investor base and attract more foreign investors, especially institutional investors, therefore, to promote liquidity in the underlying market. Up to now, Seven securities companies have been approved to become members of the Derivatives market of Hanoi Stock Exchange and connect with the derivatives trading system of Hanoi Stock Exchange including: VPBank Securities, Ho Chi Minh City Securities Corporation, Saigon Securities Inc., Vietnam Bank for Investment and Development Securities, VNDirect Securities Joint Stock Company, Viet Capital Securities JSC, MB Securities JSC. Investors can open derivatives trading accounts at those 07 securities companies. The first derivatives product on the market is the VN30Index Futures Contract. Vietnam will be the fifth country to have derivatives markets in the ASEAN region besides Singapore, Malaysia, Indonesia and Thailand and the 42nd country in the world with this high-end financial market. \\[0.5cm]
Therefore, it will open more potentiality for sort of derivatives and what this thesis tend to is the option that is is an agreement between two parties to facilitate a potential transaction on the underlying security at a preset price, referred to as the strike price, prior to the expiration date.  Pricing option is one of the most important of its surviving in trading in stock market. As a result, the mathematical techniques will be given to solve that problem. In particalar, the probability approaches will be used in this context. Firstly, the overall view of the option, is chosen, is European barrier call option with rebates that gives the holder the right but not the obligation, to buy or sell the underlying security at a specific price (the strike price) only on the option's expiration date. Especially, for barrier to make it more attractive, the trader will predict the limit of trend changing of stock price in order to reduce risk for themself and the holder have ability to reveice a part of a premium they would paid before that is called rebates. To deal with this option,  this paper is mentioned general theory related to the neccessary approaches.  The normal distribution of continuous random variables is which cannot be missed in the probability theory. Then, using the main property of Wiener process express the
random component of the model with the martingale pricing theory, which supports very powerfully for convert the real data into the mathematical techniques for solving problems easily. Then, combining the probability theory, Wiener process and Stochastic differential equation with the financial theory logically to find out the formula of the option.  Lastly, applying the option of the underlying stock into the result.  